Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-12 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised reply letter
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{flushleft}
    Mario A Medina, PhD, PE\\
    Associate Editor\\
	Solar Energy
    \end{flushleft}
\vi

@@

\indent Dear Associate Editor,
\vi

We thank you for asking us to comply with your Reviewers' reports. 
We are submitting a revised version of our manuscript entitled ``{\em \mstitle},'' by Alessandro Trindade, and Lucas Cordeiro. This revised version carefully addresses each comment provided by the reviewers, as suggested in your original decision letter. 
In particular, our reply letter describes all modifications we made to our manuscript and the respective responses to the comments raised by the reviewers.

>>>>

\begin{flushleft}
    Mario A. Medina, PhD, PE\\
    Associate Editor\\
	Solar Energy
    \end{flushleft}
\vi

@@

\indent Dear Mario,
\vi

We thank you for asking us to comply with your reviewers' reports. 
We are submitting a revised version of our manuscript entitled 
``{\em \mstitle}'' by Alessandro Trindade and Lucas Cordeiro. 
This revised version carefully addresses each comment provided 
by the reviewers, as suggested in your original decision letter. 
In particular, our reply letter describes all modifications we made 
to our manuscript and the respective responses to the comments 
raised by the reviewers.
